Adaptive Sequential Model Selection

### 2015-07-04 paper.tex
rob's changes

A natural way carry out this model selection is as follows: we compute a set  of sequential p-values   at each step of the path of models and then feed them into a stopping rule
that provides guaranteed control of the false discovery rate (FDR) or a similar quantity. Recently  \citet{gsell2013sequential} and \citet{li2015accumulation} proposed sequential stopping rules of this kind.
Both sets of rules require that once we have reached the correct model in our path, the p-values in subsequent steps are uniform (or sub-uniform)
and independent.
In this paper we develop a theoretical framework for the construction of sequential p-values  that are both (sub)-uniform and independent under the correct model,
and show how to construct them  in forward stepwise regression, LAR and the ever-active path in $\ell_1$-regularized models.
In the former case, the test is simply a sequential selective version the max-$t$ test of ~\citet{bujaxxxxmaxT}, based one the theory developed \citet{fithian2014optimal}.

@@

An outline of this paper is as follows:
In Section \ref{sec:genericSetting} we setup the problem and give some important definitions. In Section \ref{sec:sequential} we review recently proposed methods for
testing ordered hypothesis using from a sequence of p-values. These method require that the p-values be uniform and independent under the null, and we derive general conditions
to ensure this property. In Section \ref{sec:single step}  we  show how to construct valid selective $p$-values for a single step in the path and derive the max-t test
for  forward stepwise regression and the Next-$\lambda$ test for the lasso. Section \ref{sec:computation}  describes our computational strategy for estimating the p-values using accept-reject and hit and run sampling. We also relate the method to parametric bootstrap sampling. We provide a simulation study in Section \ref{sec:simulation} and briefly discuss applications of our framework to
principal components analysis in section\ref{sec:pac}. The paper ends with a Discussion.

@@

We will break the problem into two constituent subproblems. First, Section~\ref{sec:singleStep} will discuss how to obtain selective single-step $p$-values, where $p_k$ is a $p$-value for testing
\[
H_{k}:\; F\in M_{k-1}(Y)
\]
against the alternative that $F\in M_\infty\setminus M_{k-1}$. The $p$-values must account for the fact that the models are chosen adaptively. In most of our development we will make few assumptions about what form the candidate models take. Still, our results are only useful in cases where we can actually construct single-step $p$-values. At present, this largely restricts our applications to exponential family models.

Second, Section~\ref{sec:sequential} focuses on the sequential nature of the problem. \citet{gsell2013sequential} and \citet{li2015accumulation} propose stopping rules that operate on the sequence $p_{[d]}$. These stopping rules provably control certain error rates, provided that the null $p$-values are mutually independent and independent of the non-null $p$-values. We will discuss general conditions under which single-step $p$-values are independent.

\subsubsection{Linear Regression}

@@

\subsubsection{Sparse Parametric Models}\label{sec:genSparse}

@@

\subsubsection{Path Algorithms}

@@

\subsection{Which Null Hypothesis Should We Test?}
\label{sec:whichnull}

@@

In some circumstances, we might want to define a type I error at step $k$ differently. If so, we must choose a different null hypothesis to test. Let $\mu = \E Y$ and let $\theta^E$ denote the {\em least-squares coefficients} of active set $E$ --- the coefficients of the best linear predictor for the design matrix $X_E$:
\[
\theta^E = X_E^\dagger \mu = \argmin_{\theta\in \R^{|E|}} \|\mu - X_E\theta\|_2^2,
\]
where $A^\dagger$ is the Moore-Penrose pseudoinverse of the matrix $A$. Write $\proj_E\mu = X_E^\dagger \theta^E$ for the projection of $\mu$ into the column space of $X_E$.

@@

An ordered hypothesis testing procedure takes in a sequence of $p$-values $p_1, \ldots, p_d$ for null hypotheses $H_{1}, \ldots, H_{d}$, and outputs a decision $\hk$ to reject the initial block $H_{1}, \ldots, H_{\hk}$ and accept the remaining hypotheses. We will assume throughout that the hypotheses are nested with $H_{k-1} \sub H_k$. Section~\ref{sec:orderedProposals} outlines several proposals for ordered testing and discusses what error rates they control and under what conditions.

We focus on proposals from \citet{gsell2013sequential} and \citet{li2015accumulation}, all of which assume that the null hypotheses $H_{1}, \ldots, H_{d}$ are fixed, and that the null $p$-values are independent of each other and of the non-null $p$-values. Specifically, they assume that
\begin{equation}\label{eq:indepCond_fixed_k0}
\P(p_{k_0+1} \leq \alpha_{k_0+1}, \ldots, p_d \leq \alpha_d
\mid p_1, \ldots, p_{k_0}) = \prod_{i=k_0+1}^d \alpha_i,
\end{equation}
where $k_0$ is fixed.

In our problem the null hypotheses at each step are random and thus so is the completion index $k_0(Y)$. We will thus require {\em conditional} independence of null $p$-values given $k_0$:
\begin{equation}\label{eq:indepCond_random_k0}
  \P(p_{k+1} \leq \alpha_{k+1}, \ldots, p_d \leq \alpha_d
  \mid p_1, \ldots, p_k, \; k_0 = k) = \prod_{i=k+1}^d \alpha_i
\end{equation}

@@

\subsection{Stopping Rules for Ordered Testing}\label{sec:orderedProposals}

\begin{comment}
\subsubsection{BasicStop}
The most obvious procedure is simply to reject at each step until the first time that $p_k > \alpha$, which we can formalize as
\[
\hk_B(Y) = \min\left\{k \in \{1,\ldots,m\} :\;
  p_k > \alpha\right\} - 1
\]
We will call this procedure {\em BasicStop}. \WFcomment{Is there a better name for this? Can we find it in the literature?}

Selectively valid single-step $p$-values do not necessarily guarantee FWER control when $k_0$ is random. In that case, we need a bit more, but it is sufficient that we have type I error control for $p_k$ conditional on $k_0=k-1$; i.e., not just conditional on $M_{k-1}$ being a correct model, but given that $M_{k-1}$ is the {\em first} correct model.
\end{comment}

\citet{gsell2013sequential} propose another stopping rule, {\em forward stop}, that controls the FDR:
\[
  \hk_{F}(Y) = \max\left\{k \in \{1,\ldots,d\} :\;
    -\frac{1}{k}\sum_{i=1}^k \log(1-p_i) \leq \alpha\right\}
\]
ForwardStop uses the p-values{\it before} step $k$ in its decision to reject at step $k$. 
If $p_k$ is uniform then  $-\log(1-p_k)$ is an exponential random variable. If all of the null $p$-values are uniform and the others are zero, then only the null ones contribute to the sum, and
\[
\widehat{\text{FDR}}_k = -\frac{1}{k}\sum_{i=1}^k \log(1-p_i)
\]
is a Gamma random variable with mean $V/k$ and variance $V/k^2$. We stop the last time the estimate of FDR is less than $\alpha$.

\subsection{Conditions for Independence}\label{sec:pValsIndep}

The single-step $p$-value $p_k$ is selectively valid for testing $H_k:\; F \in M_{k-1}(Y)$ against $M_\infty \setminus M_{k-1}$ if, for all $F\in M_\infty$,
\[
\P_F(p_k \leq \alpha \mid M_{k-1},\; F\in M_{k-1}) \leqAS \alpha.
\]
Valid single-step selective $p$-values are not necessarily independent on nulls, but there is a simple sufficient condition under which independence on nulls is guaranteed.

@@

Two specific examples are worth discussing in detail. First, consider the {\em selective max-$t$ test}, a generalization of the max-$t$ test of ~\citet{bujaxxxxmaxT}. Controlling for $E$, the $z$-statistic for coefficient $j\notin E$ is
\begin{equation}
  z_{j,E}(Y) = \frac{(\proj_E^\perp X_j)'Y}
  {\sigma\|\proj_{E}^\perp X_j\|_2},
\end{equation}
and the $t$-statistic is
\begin{equation}
  t_{j,E}(Y) = \frac{(\proj_E^\perp X_j)'Y}
  {\hat \sigma_{j,E} \|\proj_{E}^\perp X_j\|_2},
  \qquad \text{where} \quad 
  \hat \sigma_{j,E}^2(Y) = 
  \frac{\|\proj_{E \cup \{j\}}^\perp Y\|_2^2}{n-|E|-1}.
\end{equation}
Note that $z_{j,E}$ is a monotonic function of $X_j'Y$ given $X_E'Y$, and $t_{j, E}$ is a monotonic function of $X_j'Y$ given $(X_E'Y, \|Y\|_2)$. Thus $z_{j,E}$ is measurable with respect 
to $X_{E \cup \{j\}}'Y$ if $\sigma^2$ is known, and otherwise $t_{j,E}$ is measurable with respect to $(X_{E \cup \{j\}}'Y, \|Y\|_2)$.

@@

\begin{figure}
  \centering
  % source code: ??? for simulation, sparseSim.R for plotting
  \includegraphics[width=.8\textwidth]{figs/simulation_snr_5_alpha_05_null_false.pdf}
  \caption{\em CDFs of saturated-model (black), selected-model (red), and nominal (blue) $p$-values in the simulation of Section~\ref{sec:sparseReg}, conditional on testing a false null hypothesis at step $k$. The selected-model test is much more powerful than the saturated-model test. The nominal test appears powerful, but is not a correct $p$-value.}
  \label{fig:simulation_null_false}
\end{figure}

\begin{figure}
  \centering
  % source code: ??? for simulation, sparseSim.R for plotting
  \includegraphics[width=.8\textwidth]{figs/simulation_snr_5_alpha_05_null_true.pdf}
  \caption{\em CDFs of saturated-model (black), selected-model (red), and nominal (blue) $p$-values in the simulation of Section~\ref{sec:sparseReg}, conditional on testing a true null hypothesis at step $k$. The selected-model test is much more powerful than the saturated-model test. The nominal test is badly anti-conservative.}
  \label{fig:simulation_null_true}
\end{figure}

\begin{figure}
  \centering
  % source code: ??? for simulation, sparseSim.R for plotting
  \includegraphics[width=.8\textwidth]{figs/simulation_snr_5_alpha_05_noise_var.pdf}
  \caption{\em CDFs of saturated-model (black), selected-model (red), and nominal (blue) $p$-values in the simulation of Section~\ref{sec:sparseReg}, conditional on the event that the variable added at step $k$ is a noise variable in the full model. Here, none of the methods produce uniform $p$-values. The null hypothesis is false in most cases and so --- in our model-centric point of view --- rejection is the desired outcome.}
  \label{fig:simulation_noise_var}
\end{figure}

@@

% latex table generated in R 3.0.2 by xtable 1.7-1 package
% Fri May  1 09:29:28 2015
\begin{table}[ht]
  \centering
  \begin{tabular}{llcccc}
    \hline
    Method & Stopping Rule & $p_{\text{screen}}$ & $\text{FWER}_{\text{mod}}$ an
    & $\text{FDR}_{\text{mod}}$ 
    & $\text{FDR}_{\text{var}}$ \\ 
    \hline
    Selected & Basic & .290 & .000 & .002 & .039 \\ 
    Selected & Forward & .559 & .027 & .020 & .066 \\ 
    Selected & Strong & .041 & .014 & .008 & .042 \\ 
    \hline
    Saturated & Basic & .000 & .000 & .000 & .028 \\ 
    Saturated & Forward & .014 & .000 & .000 & .030 \\ 
    Saturated & Strong & .000 & .000 & .000 & .032 \\ 
    \hline
    Knockoffs & & .000 & --- & --- & .231 \\ 
    \hline
  \end{tabular}
  \caption{\WFcomment{Comment on results once they are correct. These numbers are wrong right now.}}
\end{table}

\section{Principal Components Analysis}
\label{sec:pca}

>>>>

A natural way carry out this model selection is as follows: we compute a set  of sequential p-values   at each step of the path of models and then feed them into a stopping rule
that provides guaranteed control of the false discovery rate (FDR) or a similar quantity. Recently  \citet{gsell2013sequential} and \citet{li2015accumulation} proposed sequential stopping rules of this kind.
Both sets of rules require that once we have reached the correct model in our path, the p-values in subsequent steps are uniform (or sub-uniform)
and independent.
In this paper we develop a theoretical framework for the construction of sequential p-values  that are both (sub)-uniform and independent under the correct model,
and show how to construct them  in forward stepwise regression, LAR and the ever-active path in $\ell_1$-regularized models.
In the former case, the test is simply a sequential selective version the max-$t$ test of ~\citet{buja2014}, based on the theory developed \citet{fithian2014optimal}.

@@

An outline of this paper is as follows:
In Section \ref{sec:genericSetting} we setup the problem and give some important definitions. In Section \ref{sec:sequential} we review recently proposed methods for
testing ordered hypothesis using from a sequence of p-values. These method require that the p-values be uniform and independent under the null, and we derive general conditions
to ensure this property. In Section \ref{sec:singleStep}  we  show how to construct valid selective $p$-values for a single step in the path and derive the max-t test
for  forward stepwise regression and the Next-$\lambda$ test for the lasso. Section \ref{sec:computation}  describes our computational strategy for estimating the p-values using accept-reject and hit and run sampling. We also relate the method to parametric bootstrap sampling. We provide a simulation study in Section \ref{sec:simulation} and briefly discuss applications of our framework to
principal components analysis in section\ref{sec:pac}. The paper ends with a Discussion.

@@

First suppose that we have single step p-values for testing
\[
H_{k}:\; F\in M_{k-1}(Y)
\]
against the alternative that $F\in M_\infty\setminus M_{k-1}$. The $p$-values must account for the fact that the models are chosen adaptively. 
\citet{gsell2013sequential} and \citet{li2015accumulation} propose stopping rules that operate on the sequence $p_{[d]}$. These stopping rules provably control certain error rates, provided that the null $p$-values are mutually independent and independent of the non-null $p$-values. 
We review these methods in Section~\ref{sec:sequential} .

Hence the task is to  construct sequential p-values which satisfy the above requirements, and we do this in Section \ref{sec:singleStep}.
We also discuss general conditions under which single-step $p$-values are independent.

\subsection{Linear Regression}

@@

\subsection{Sparse Parametric Models}\label{sec:genSparse}

@@

\subsection{Path Algorithms}

@@

\subsection{``Model-centric'' and ``variable-centric'' null hypotheses}
\label{sec:whichnull}

@@

In some circumstances, we might want to define a type I error at step $k$ differently. If so, we must choose a different null hypothesis to test. Let $\mu = \E Y$ and let $\theta^E$ denote the {\em least-squares coefficients} of active set $E$ --- the coefficients of the best linear predictor for the design matrix $X_E$:
\[
\theta^E = X_E^\dagger \mu = \argmin_{\theta\in \R^{|E|}} \|\mu - X_E\theta\|_2^2,
\]
where $A^\dagger$ is the Moore-Penrose pseudoinverse of the matrix $A$. 
These are the true ``partial regression coefficients''  for design matrix $X_E$.
 Write $\proj_E\mu = X_E^\dagger \theta^E$ for the projection of $\mu$ into the column space of $X_E$.

@@

An ordered hypothesis testing procedure takes in a sequence of $p$-values $p_1, \ldots, p_d$ for null hypotheses $H_{1}, \ldots, H_{d}$, and outputs a decision $\hk$ to reject the initial block $H_{1}, \ldots, H_{\hk}$ and accept the remaining hypotheses. We will assume throughout that the hypotheses are nested with $H_{k-1} \sub H_k$. The next Section outlines several proposals for ordered testing and discusses what error rates they control and under what conditions.

\subsection{Stopping Rules for Ordered Testing}
\label{sec:orderedProposals}

\subsubsection{BasicStop}
The most obvious procedure is simply to reject at each step until the first time that $p_k > \alpha$, which we can formalize as
\[
\hk_B(Y) = \min\left\{k \in \{1,\ldots,m\} :\;
  p_k > \alpha\right\} - 1
\]
We will call this procedure {\em BasicStop}. 
It is discussed in \citet{marcus1976}.

Selectively valid single-step $p$-values do not necessarily guarantee FWER control when $k_0$ is random. In that case, we need a bit more, but it is sufficient that we have type I error control for $p_k$ conditional on $k_0=k-1$; i.e., not just conditional on $M_{k-1}$ being a correct model, but given that $M_{k-1}$ is the {\em first} correct model.

\citet{gsell2013sequential} propose another stopping rule, {\em forward stop}, that controls the FDR:
\[
  \hk_{F}(Y) = \max\left\{k \in \{1,\ldots,d\} :\;
    -\frac{1}{k}\sum_{i=1}^k \log(1-p_i) \leq \alpha\right\}
\]
ForwardStop uses the p-values {\it before} step $k$ in its decision to reject at step $k$. 
If $p_k$ is uniform then  $-\log(1-p_k)$ is an exponential random variable. If all of the null $p$-values are uniform and the others are zero, then only the null ones contribute to the sum, and
\[
\widehat{\text{FDR}}_k = -\frac{1}{k}\sum_{i=1}^k \log(1-p_i)
\]
is a Gamma random variable with mean $V/k$ and variance $V/k^2$. We stop the last time the estimate of FDR is less than $\alpha$.

\subsection{Random hypotheses}
The forementioned proposals of  \citet{gsell2013sequential} and \citet{li2015accumulation}, all assume that the null hypotheses $H_{1}, \ldots, H_{d}$ are fixed, and that the null $p$-values are independent of each other and of the non-null $p$-values. Specifically, they assume that
\begin{equation}\label{eq:indepCond_fixed_k0}
\P(p_{k_0+1} \leq \alpha_{k_0+1}, \ldots, p_d \leq \alpha_d
\mid p_1, \ldots, p_{k_0}) = \prod_{i=k_0+1}^d \alpha_i,
\end{equation}
where $k_0$ is fixed.

in our problem the null hypotheses at each step are random and thus so is the completion index $k_0(Y)$. We will thus require {\em conditional} independence of null $p$-values given $k_0$:
\begin{equation}\label{eq:indepCond_random_k0}
  \P(p_{k+1} \leq \alpha_{k+1}, \ldots, p_d \leq \alpha_d
  \mid p_1, \ldots, p_k, \; k_0 = k) = \prod_{i=k+1}^d \alpha_i
\end{equation}

@@

\section{Conditions for Independence of p-values}\label{sec:pValsIndep}

We say that the  single-step $p$-value $p_k$ is selectively valid for testing $H_k:\; F \in M_{k-1}(Y)$ against $M_\infty \setminus M_{k-1}$ if, for all $F\in M_\infty$,
\[
\P_F(p_k \leq \alpha \mid M_{k-1},\; F\in M_{k-1}) \leqAS \alpha.
\]
Valid single-step selective $p$-values are not necessarily independent on nulls, but there is a simple sufficient condition under which independence on nulls is guaranteed.

@@

Two specific examples are worth discussing in detail. First, consider the {\em selective max-$t$ test}, a generalization of the max-$t$ test described in 
~\citet{buja2014}. Controlling for $E$, the $z$-statistic for coefficient $j\notin E$ is
\begin{equation}
  z_{j,E}(Y) = \frac{(\proj_E^\perp X_j)'Y}
  {\sigma\|\proj_{E}^\perp X_j\|_2},
\end{equation}
and the $t$-statistic is
\begin{equation}
  t_{j,E}(Y) = \frac{(\proj_E^\perp X_j)'Y}
  {\hat \sigma_{j,E} \|\proj_{E}^\perp X_j\|_2},
  \qquad \text{where} \quad 
  \hat \sigma_{j,E}^2(Y) = 
  \frac{\|\proj_{E \cup \{j\}}^\perp Y\|_2^2}{n-|E|-1}.
\end{equation}
Note that $z_{j,E}$ is a monotonic function of $X_j'Y$ given $X_E'Y$, and $t_{j, E}$ is a monotonic function of $X_j'Y$ given $(X_E'Y, \|Y\|_2)$. Thus $z_{j,E}$ is measurable with respect 
to $X_{E \cup \{j\}}'Y$ if $\sigma^2$ is known, and otherwise $t_{j,E}$ is measurable with respect to $(X_{E \cup \{j\}}'Y, \|Y\|_2)$.

@@

\begin{figure}[h]
  \centering
  % source code: ??? for simulation, sparseSim.R for plotting
  \includegraphics[width=1\textwidth]{figs/simulation_snr_5_alpha_05_null_false.pdf}
  \caption{\em  CDFs of nominal (black), MaxT (red), MaxT with unknown $\sigma$ (green) and  saturated-model (blue) $p$-values in the simulation of Section~\ref{sec:sparseReg}, conditional on testing a false null hypothesis at step $k$. The MaxT approaches are much more powerful than the saturated-model test. The nominal test appears to be powerful, 
  but is not $U(0,1)$ under the null, as shown below in Figure \ref{fig:simulation_null_true}.}
  \label{fig:simulation_null_false}
\end{figure}

\begin{figure}[h]
  \centering
  % source code: ??? for simulation, sparseSim.R for plotting
  \includegraphics[width=1\textwidth]{figs/simulation_snr_5_alpha_05_null_true.pdf}
  \caption{\em  CDFs of nominal (black), MaxT (red), MaxT with unknown $\sigma$ (green) and  saturated-model (blue) p-values in the simulation of Section~\ref{sec:sparseReg}, conditional on testing a true null hypothesis at step $k$.  The nominal test is badly anti-conservative, while all of the other methods  show uniform p-values as desired.}
  \label{fig:simulation_null_true}
\end{figure}

\begin{figure}[h]
  \centering
  % source code: ??? for simulation, sparseSim.R for plotting
  \includegraphics[width=1\textwidth]{figs/simulation_snr_5_alpha_05_noise_var.pdf}
  \caption{\em CDFs of nominal (black), MaxT (red), MaxT with unknown $\sigma$ (green) and  saturated-model (blue) $p$-values in the simulation of Section~\ref{sec:sparseReg}, conditional on the event that the variable added at step $k$ is a noise variable in the full model. Here, none of the methods produce uniform $p$-values. The null hypothesis is false in most cases and so --- in our model-centric point of view --- rejection is the desired outcome.}
  \label{fig:simulation_noise_var}
\end{figure}

@@

% latex table generated in R 3.0.2 by xtable 1.7-1 package
% Fri May  1 09:29:28 2015
%\begin{table}[ht]
 % \centering
 % \begin{tabular}{llcccc}
  %  \hline
  %  Method & Stopping Rule & $p_{\text{screen}}$ & $\text{FWER}_{\text{mod}}$ an
 %   & $\text{FDR}_{\text{mod}}$ 
  %  & $\text{FDR}_{\text{var}}$ \\ 
 %   \hline
    %Selected & Basic & .290 & .000 & .002 & .039 \\ 
   % Selected & Forward & .559 & .027 & .020 & .066 \\ 
   % Selected & Strong & .041 & .014 & .008 & .042 \\ 
  %  \hline
   % Saturated & Basic & .000 & .000 & .000 & .028 \\ 
  %  Saturated & Forward & .014 & .000 & .000 & .030 \\ 
  %  Saturated & Strong & .000 & .000 & .000 & .032 \\ 
  %  \hline
  %  Knockoffs & & .000 & --- & --- & .231 \\ 
  %  \hline
 % \end{tabular}
 % \caption{\WFcomment{Comment on results once they are correct. These numbers are wrong right now.}}
%\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
  Method, Stopping rule& $p_{\text screen}$ & FWER$_{\text mod}$ & FDR$_{\text mod}$ &FDR$_{\text var}$ \\
% & \$p\_\{$\backslash$text\{screen\}\} & \$$\backslash$text\{FWER\}\_\{$\backslash$text\{model\}\}\$ & \$$\backslash$text\{FDR\}\_\{$\backslash$text\{model\}\}\$ & \$$\backslash$text\{FDR\}\_\{$\backslash$text\{variable\}\}\$ \\ 
  \hline
Nominal, Simple & 0.832 & 0.252 & 0.097 & 0.171 \\ 
  Nominal, Forward & 0.931 & 0.896 & 0.345 & 0.426 \\ 
  Nominal, Strong & 0.003 & 0.000 & 0.000 & 0.035 \\ 
  \hline
  MaxT, Simple & 0.369 & 0.000 & 0.002 & 0.042 \\ 
  MaxT, Forward & 0.668 & 0.038 & 0.026 & 0.080 \\ 
  MaxT, Strong & 0.025 & 0.006 & 0.004 & 0.038 \\ 
  \hline
  MaxT-Identify, Simple & 0.404 & 0.000 & 0.002 & 0.042 \\ 
  MaxT-Identify, Forward & 0.688 & 0.039 & 0.026 & 0.082 \\ 
  MaxT-Identify, Strong & 0.024 & 0.003 & 0.002 & 0.037 \\ 
  \hline
  Saturated, Simple & 0.000 & 0.000 & 0.000 & 0.029 \\ 
  Saturated, Forward & 0.013 & 0.001 & 0.000 & 0.030 \\ 
  Saturated, Strong & 0.000 & 0.000 & 0.000 & 0.033 \\ 
  \hline
  Knockoffs & 0.252 &  &  & 0.103 \\ 
   \hline
\end{tabular}
\end{table}

We see that 1) strongStop and forwardStop control FWER and modelwise FDR, respectively, using p-values from MaxT or MaxT-identify, as predicted by theory
2) the nominal p-values do not lead to control of FWER or FDR, as expected, 3) the pvalues from the saturated model show FWER and modelwise-FDR control,
although not guaranteed by theory, 4) the MaxT rules show higher probabilities of selecting the true model, especially using forwardStop, 5) the knockoff method
does not yields variable-wise FDR control, as it should.
5)
\section{Principal Components Analysis}
\label{sec:pca}
